---
title: "Quantitative strategies on High Frequency Data"
subtitle: "PRESENTATION"
author: "Elgun Ismayilov"
date: "Academic year 2024/2025"
output: slidy_presentation
fontsize: 12pt
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, error = FALSE, message = FALSE,
                      warning = FALSE)
```

```{r, include=FALSE}
library(kableExtra) #for tables
```

```{r, echo = FALSE}
result <- read.csv("/Users/elgun/Desktop/Quantitative-strategies-on-High-Frequency-Data/result.csv")
```


# Introduction

In this project, we implement two simple trading strategies for a single asset: the NASDAQ index futures contract.

## Strategy 1: Exponential Moving Average (EMA)

This strategy uses a 120-period EMA. The trading logic is as follows:

- If, at time \( t_{i-1} \), the asset's price is higher than the EMA, a buy order is placed.

- Otherwise, a sell order is executed at time \( t_i \).

## Strategy 2: EMA with Volatility Band

This strategy uses a 60-period EMA along with a volatility band based on a 120-period window. The trading logic is as follows:

- If, at time \( t_{i-1} \), the asset's price is greater than the EMA plus the volatility band, a buy order is placed.

- Otherwise, a sell order is executed.

# Performance Analysis of EMA 120 window


```{r, echo = F}
# Create the kable object with the first 9 columns
kable(result[, 1:9], "html", digits = 6, align = "r") %>%
  kable_styling(font_size = 12, full_width = FALSE) %>%
  column_spec(1:9, width = "12em", color = "darkgreen") %>% 
  row_spec(0, bold = TRUE, color = "navy", background = "lightgray")  

```


## Profitability Overview

**First period** shows a positive cumulative net profit (42,429.88), indicating successful strategy execution.

**Remaining periods** exhibit consistent losses, with the fifth period suffering the largest cumulative net loss (-44,017.80).

## Risk Metrics Evaluation

**Sortino Ratio** (-0.038804): Negative value signals that downside risk dominates returns, leading to poor risk-adjusted performance.

**Calmar Ratio** (-0.009086): Highlights significant drawdowns, suggesting the strategy fails to sustain long-term profitability.

**Cumulative net profit** (-69,383.76): The overall strategy is losing money, confirming an ineffective approach.

## Trade Frequency & Performance Correlation

**Higher trade frequency** (Avg_nTrades_EMA_120) does not equate to better performance.

**Fifth Period** has high trade frequency (0.096064) but incurs largest loss (-44,017.80).

**Best-performing period** (first period) has a moderate trade frequency (0.083263), indicating trade quality matters more than quantity.

# Performance Analysis of EMA 60 and SD 120 Window


```{r, echo = F}
# Create the kable object with the first column and columns from the 10th onward
kable(result[, c(1, 10:ncol(result))], "html", digits = 6, align = "r") %>%
  kable_styling(font_size = 12, full_width = FALSE) %>%
  column_spec(1:ncol(result[, c(1, 10:ncol(result))]), width = "12em", color = "darkgreen") %>%  # Apply styling to selected columns
  row_spec(0, bold = TRUE, color = "navy", background = "gray")  # Style the header row



```


## Quarterly Performance Analysis

### **Best Performing Period**
- **2022 Q1**:
  - **Cumulative Gross Profit**: Highest at **85,882.60**, reflecting strong financial performance.
  - Positive performance metrics:
    - **Gross_CR_SD_EMA**: **0.070587**
    - **Net_CR_SD_EMA**: **0.066517**
    - **Gross_SR_SD_EMA**: **0.024020**
    - **Net_SR_SD_EMA**: **0.022794**

### **Worst Performing Period**
- **2023 Q2**:
  - **Cumulative Gross Profit**: Lowest at **-17,923.52**, highlighting a challenging quarter.
  - Negative performance metrics:
    - **Gross_CR_SD_EMA**: **-0.009856**
    - **Net_CR_SD_EMA**: **-0.009987**
    - **Gross_SR_SD_EMA**: **-0.010208**
    - **Net_SR_SD_EMA**: **-0.012907**

### **Other Performance Trends**
1. **Moderate Positive Quarters**:
   - **2023 Q4**: Gross profit of **7,762.00** with consistent positive metrics.
   - **2024 Q1**: Cumulative gross profit of **9,343.56**, maintaining improvement.
2. **Reversion to Negative**:
   - **2024 Q2**: Cumulative gross profit dropped to **-8,622.10**, with a return to negative performance metrics.

## Performance Metrics Overview

1. **Net Sortino Ratio**:  
   - Minimal downside risk-adjusted returns at **0.000633**.

2. **Net Calmar Ratio**:  
   - A relatively low value of **0.047944**, suggesting limited risk-adjusted performance relative to drawdowns.

3. **Cumulative net profit**:  
   - Total cumulative profit is **33,465.62**, indicating overall positive performance.

4. **Average Trade Profitability**:  
   - An average trade value of **0.592938**, showing moderate per-trade profitability.

5. **Summary Statistic**:  
   - A value of **0.355229**, reflecting balanced overall performance across periods.

# **Conclusion**

## **Overall Performance**
- The **first strategy** (EMA) resulted in a **total cumulative net loss of -69,383.76**, with consistently negative performance across most periods. The **only profitable quarter** was the first, highlighting the lack of long-term sustainability for this approach.
- The **second strategy** (EMA with Volatility Band) yielded a **modest cumulative net profit of 33,465.62**, showing better resilience and periodic recovery (e.g., **2023 Q4** and **2024 Q1**). However, overall profitability remains suboptimal due to volatility and inconsistent results.

## **Key Strengths and Weaknesses**
1. **Strengths**:
   - **Second Strategy (Volatility Band)** demonstrated periods of profitability (notably **2022 Q1**) and positive performance metrics like the **Net Calmar Ratio** (0.047944).
2. **Weaknesses**:
   - Both strategies suffered from poor **risk-adjusted performance**, as indicated by the low or negative **Sortino** and **Calmar Ratios**.
   - Sustained losses in multiple periods, especially **2023 Q2**, undermined cumulative gains.

## **Risk-Adjusted Metrics**
- The **Sortino Ratio** for both strategies was low or negative, indicating poor downside risk-adjusted returns.
- The **Net Calmar Ratio** for the second strategy (0.047944) was slightly positive but insufficient for long-term reliability.

## **Decision**
- Based on the analysis, I choose the **second strategy (EMA with Volatility Band)**. The positive cumulative net profit and better overall metrics make it a more viable option compared to the first strategy.

